### 2017-12-15 manuscript.rmd
added section on different types of monoecy

The phylogenetic relationships recovered in this study are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (Fig. 3) [@Dunn:2005dy]. There is strong support for the Cystonectae as sister to all other siphonophores, the Codonophora. We also find strong support for Calycophorae nested within the paraphyletic "Physonectae", and for the Apolemidae as sister to all other codonophorans. Multiple nodes that were not resolved in the previous two-gene analysis receive strong support in this 1,071-gene transcriptome analysis. There is strong support for the Pyrostephidae as sister to all other non-apolemiid codonophorans. Within the clade that is sister to the Pyrostephidae, we find two main clades, the Calycophorae and a clade we call the Euphysonectae (Fig. 3), which includes the remaining non-apolemiid, non-pyrostephid "Physonectae". We define the Euphysonectae as the clade consisting of *Agalma elegans* and all taxa that are more closely related to it than to *Diphyes dispar*. Within Euphysonectae, we identify Clade A and Clade B (Fig. 3). Clade A is a group of siphonophores that all have an involucrum, or fold, that forms around the base of the tentilla [@totton1965synopsis]. This clade also shares the prescence of a descending mantle canal within the nectophores (Fig. S6), and is also monoecious (Fig. 5). Clade B is a group of deep-sea siphonophores found within the bathypelagic. Within Clade B there is low support for the placement of *Erenna richardi*, and more taxon sampling will be required to determine the relationship of species within this clade.

@@

Siphonophore colonies are either monoecious (male and female gonophores are on the same colony) or dioecious (male and female gonophores are on different colonies). The current better-resolved tree (Fig. 5A), indicates that monoecy in siphonophores evolved twice from a dioecious ancestor, in the branch leading to Calycophorae and in the branch leading to Clade A. There is a small probability for an alternative scenario featuring a single gain of monoecy before the split of Codonophora, with a subsequent shift to dioecy in the *Marrus-Erenna* clade. Previous analyses suggested that the common ancestor of siphonophores was dioecious, and there is a single gain of monoecy within the Codonophora [@Dunn:2005dy].

>>>>

The phylogenetic relationships recovered in this study are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (Fig. 3) [@Dunn:2005dy]. There is strong support for the Cystonectae as sister to all other siphonophores, the Codonophora. We also find strong support for Calycophorae nested within the paraphyletic "Physonectae", and for the Apolemidae as sister to all other codonophorans. Multiple nodes that were not resolved in the previous two-gene analysis receive strong support in this 1,071-gene transcriptome analysis. There is strong support for the Pyrostephidae as sister to all other non-apolemiid codonophorans. Within the clade that is sister to the Pyrostephidae, we find two main clades, the Calycophorae and a clade we call the Euphysonectae (Fig. 3), which includes the remaining non-apolemiid, non-pyrostephid "Physonectae". We define the Euphysonectae as the clade consisting of *Agalma elegans* and all taxa that are more closely related to it than to *Diphyes dispar*. Within Euphysonectae, we identify Clade A and Clade B (Fig. 3). Clade A is a group of siphonophores that all have an involucrum, or fold, that forms around the base of the tentilla [@totton1965synopsis]. This clade also shares the prescence of a descending mantle canal within the nectophores (Fig. S6), and is also monoecious (Fig. 5). Within Clade B there is low support for the placement of *Erenna richardi*, and more taxon sampling will be required to determine the relationship of species within this clade.

@@

In all siphonophores, each gonophoren(sexual medusa that produces gametes) is either male or female. Siphonophore colonies are either monoecious (male and female gonophores are on the same colony) or dioecious (male and female gonophores are on different colonies). The current better-resolved tree (Fig. 5A), indicates that monoecy in siphonophores evolved twice from a dioecious ancestor, in the branch leading to Calycophorae and in the branch leading to Clade A. There is a small probability for an alternative scenario featuring a single gain of monoecy before the split of Codonophora, with a subsequent shift to dioecy in the *Marrus-Erenna* clade. Previous analyses suggested that the common ancestor of siphonophores was dioecious, and there is a single gain of monoecy within the Codonophora [@Dunn:2005dy].

The Calycophorae and Clade A each have very different arangements of monoecy, providing evidence for multiple gains of monoecy. In both the Calycophorae and Clade A, male and female gonophores are located within the same colony. In calycophorans, each cormidium (a single reiterated sequence of zooids along the stem, see Fig. 2) bears either male or female zooids. In this form of monoecy, the male and female cormidia can either be in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. In Clade A, however, male and female zooids are found within the same cormidium.In these species, the male and female zooids are placed at very different but well defined locations within the cormidium.
